% !TeX root = ../thuthesis-example.tex

% 中英文摘要和关键字

\begin{abstract}
  多重部分子散射（MPS）是探索质子内部部分子横向空间分布和关联的核心探针。
  在独立散射近似下，MPS 过程的有效截面 $\sigma_{\mathrm{eff}}$ 概括了这些非微扰信息。
  然而，不同末态对 $\sigma_{\mathrm{eff}}$ 的测量结果存在显著差异，表明简化的因子化图像需要来自更多样化末态的检验。
  本论文基于 CMS 实验在 Run~3 期间采集的 $\sqrt{s}=\SI{13.6}{\tera\eV}$ 质子--质子对撞数据，
  对双重夸克偶素联合矢量介子$\phi(1020)$产生过程 $pp \to J/\psi + J/\psi + \phi + X$ 进行了首次观测，
  积分亮度为 $\SI{289.21}{\per\femto\barn}$。
  $\phi$ 介子作为含 $s\bar{s}$ 的轻味矢量介子，为 MPS 研究提供了不同于纯重夸克偶素末态的独立检验道。

  两个 $J/\psi$ 候选通过 $J/\psi \to \mu^+\mu^-$ 衰变道重建，$\phi$ 候选通过 $\phi \to K^+K^-$ 衰变道重建。
  经完整选择流程后，共获得 $4.8829\times10^4$ 个 $J/\psi J/\psi \phi$ 候选事例。
  通过对 $m(\mu^+\mu^-)_1$、$m(\mu^+\mu^-)_2$ 和 $m(K^+K^-)$ 三维不变质量谱的无分箱最大似然拟合，
  提取原始信号产额 $N_{sss}=(1.563\pm0.143)\times10^3$，信号统计显著性为 $12.0\,\sigma$。
  基于蒙特卡罗模拟，计算了逐分箱的几何接受度和条件效率修正因子，
  并利用 sPlot 技术实现了信号与本底在运动学分布中的统计分离。
  经效率修正后的总信号产额为 $N_{sss}^{\mathrm{corr}} = 9.35 \times 10^4 \pm 1.94 \times 10^4\,(\mathrm{stat}) \pm 1.76 \times 10^4\,(\mathrm{syst,\,partial})$，
  对应的产生截面为 $\sigma(pp \to J/\psi J/\psi \phi + X) \times \mathcal{B}^2(J/\psi \to \mu^+\mu^-) \times \mathcal{B}(\phi \to K^+K^-) = 323 \pm 67\,(\mathrm{stat}) \pm 61\,(\mathrm{syst,\,partial})~\SI{}{\femto\barn}$
  和 $\sigma(pp \to J/\psi J/\psi \phi + X) = 182 \pm 38\,(\mathrm{stat}) \pm 34\,(\mathrm{syst,\,partial})~\SI{}{\pico\barn}$。
  论文建立了涵盖信号提取、效率修正、候选重建和样本建模等环节的系统误差评估框架，
  当前传播的18.8\%系统误差仅反映采用不同子过程蒙特卡罗样本构造效率图所引起的变化，其余系统误差源尚待完成定量验证。

  本分析首次在含有一个轻味矢量介子的三粒子末态中观测到 MPS 信号，
  为检验因子化 MPS 图像在多种末态中的普适性提供了新的实验依据。
  所建立的分析框架可直接服务于后续截面测量和有效截面 $\sigma_{\mathrm{eff}}$ 的提取。

  \thusetup{
    keywords = {多重部分子散射, 三夸克偶素联合产生, $J/\psi$ 介子, $\phi$ 介子, CMS实验},
  }
\end{abstract}

\begin{abstract*}
  Multiple parton scattering (MPS) is a key probe of the transverse spatial distribution
  and correlations of partons inside the proton. Under the independent-scattering
  approximation, the effective cross section $\sigma_{\mathrm{eff}}$ encapsulates these
  non-perturbative properties. However, $\sigma_{\mathrm{eff}}$ values extracted from
  different final states show significant discrepancies, indicating that the simplified
  factorisation picture requires testing with more diverse final states.
  This thesis presents the first observation of the triple-quarkonium production process
  $pp \to J/\psi + J/\psi + \phi + X$ in proton--proton collisions at $\sqrt{s}=\SI{13.6}{\tera\eV}$
  using data collected by the CMS experiment during LHC Run~3, corresponding to an
  integrated luminosity of $\SI{289.21}{\per\femto\barn}$.
  The $\phi$ meson, a light $s\bar{s}$ vector meson, provides an independent probe
  for MPS studies distinct from pure heavy-quarkonium final states.

  Two $J/\psi$ candidates are reconstructed via the $J/\psi \to \mu^+\mu^-$ decay channel,
  and the $\phi$ candidate via $\phi \to K^+K^-$.
  After the full selection, $4.8829\times10^4$ $J/\psi J/\psi \phi$ candidates are obtained.
  A three-dimensional unbinned maximum-likelihood fit to the $m(\mu^+\mu^-)_1$,
  $m(\mu^+\mu^-)_2$, and $m(K^+K^-)$ invariant-mass distributions yields a raw signal yield
  of $N_{sss}=(1.563\pm0.143)\times10^3$, with a statistical significance of $12.0\,\sigma$.
  Per-bin geometric acceptance and conditional efficiency correction factors are
  evaluated using Monte Carlo simulation, and the sPlot technique is employed to
  statistically separate signal and background in kinematic distributions.
  The efficiency-corrected total signal yield is $N_{sss}^{\mathrm{corr}} = 9.35 \times 10^4 \pm 1.94 \times 10^4\,(\mathrm{stat}) \pm 1.76 \times 10^4\,(\mathrm{syst,\,partial})$,
  corresponding to a production cross section of
  $\sigma(pp \to J/\psi J/\psi \phi + X) \times \mathcal{B}^2(J/\psi \to \mu^+\mu^-) \times \mathcal{B}(\phi \to K^+K^-) = 323 \pm 67\,(\mathrm{stat}) \pm 61\,(\mathrm{syst,\,partial})~\SI{}{\femto\barn}$
  and $\sigma(pp \to J/\psi J/\psi \phi + X) = 182 \pm 38\,(\mathrm{stat}) \pm 34\,(\mathrm{syst,\,partial})~\SI{}{\pico\barn}$.
  A systematic-uncertainty evaluation framework is established, covering signal extraction,
  efficiency corrections, candidate reconstruction, and sample modelling,
  The currently propagated 18.8\% component only quantifies the variation obtained
  from efficiency maps constructed with different subprocess Monte Carlo samples;
  the remaining systematic sources still require quantitative validation.

  This analysis provides the first observation of MPS signals in a three-particle final
  state containing a light-flavour vector meson, offering new experimental input for
  testing the universality of the factorised MPS picture across diverse final states.
  The analysis framework established in this thesis lays the groundwork for subsequent
  cross-section measurements and extraction of the effective cross section $\sigma_{\mathrm{eff}}$.

  \thusetup{
    keywords* = {Multiple parton scattering, Triple-quarkonium production, $J/\psi$ meson, $\phi$ meson, CMS experiment},
  }
\end{abstract*}
